Practice proofs \#9

### 2018-09-04 practice-proofs/EH6.tex
Added files for practice proofs 4-9.

\subsection*{Cardinality and subsets}

\begin{prop} \label{prop:SubsetCardinality}
	If $X\subset Y$, then $\# X\leq \# Y$.
\end{prop}

\hintbox{
	Directly construct an injection $f:X\to Y$.
	If the codomain of $f$ was $X$, then you could choose a bijection quite easily.
	What happens if you expand the codomain back to $Y$?
}

\subsection*{Countable unions of sets}

@@

\begin{lem} \label{lem:CountableUnions1}
	If $\#A=\#B=\aleph_0$, then $\#(A\times B)=\aleph_0$.
\end{lem}

@@

\begin{prop} \label{prop:CountableUnions2}
	If, for each $j\in J$, $A_j$ is a nonempty set with cardinality $\#A_j\leq\aleph_0$, and $\#J=\aleph_0$, then
	$$
		\# \bigsqcup_{j\in J} A_j = \aleph_0.
	$$
\end{prop}

@@

\begin{prop} \label{prop:CountableUnions3}
	If, for each $j\in J$, $\#A_j\leq\aleph_0$, and $\#J=\aleph_0$, then
	$$
		\# \bigcup_{j\in J} A_j \leq \aleph_0.
	$$
\end{prop}

\hintbox{
	Direct construction of a surjection from the disjoint union of the previous proposition to this ordinary union.
}

\subsection*{Cardinality and power sets}

We say that two sets are \emph{equinumerous} if they have the same cardinality. The following proposition says that the operation ``take the power set'' preserves equinumerosity.

\begin{prop} \label{prop:PowerSetsPreserveEquinumerosity}
	Suppose $\# X=\# Y$. Then $\# \power(X)=\# \power(Y)$. Moreover, if $\# X\leq\# Y$, then $\# \power(X)\leq\# \power(Y)$.
\end{prop}

\hintbox{
	There must be a bijection $f:X\to Y$. Pick an arbitrary $S\subset X$.
	Think about the process of taking the image of $S$ in $f$.
	Is that a function of $S$? Showing injectivity / surjectivity requires you to exploit injectivity / surjectivity of $f$.

	It is probably more efficient to prove the second part first.
}

>>>>

@@

\begin{lem} \label{lem:CardinalityUnions1}
	If $\#A=\#B=\aleph_0$, then $\#(A\times B)=\aleph_0$.
\end{lem}

@@

\begin{prop} \label{prop:CardinalityUnions2}
	If, for each $j\in J$, $A_j$ is a nonempty set with cardinality $\#A_j\leq\aleph_0$, and $\#J=\aleph_0$, then
	$$
		\# \bigsqcup_{j\in J} A_j = \aleph_0.
	$$
\end{prop}

@@

\begin{prop} \label{prop:CardinalityUnions3}
	If, for each $j\in J$, $\#A_j\leq\aleph_0$, and $\#J=\aleph_0$, then
	$$
		\# \bigcup_{j\in J} A_j \leq \aleph_0.
	$$
\end{prop}

\hintbox{
	Direct construction of a surjection from the disjoint union appearing in proposition~\ref{prop:CardinalityUnions2} to this ordinary union.
}

### 2018-09-04 practice-proofs/PracticeProofs5.tex
Added files for practice proofs 4-9.

@@

\hintbox{
	Directly construct an injection $f:X\to Y$.
	If the codomain of $f$ was $X$, then you could choose a bijection quite easily.
	What happens if you expand the codomain back to $Y$?
}

@@

\hintbox{
	Stitch together some bijections that must exist, to produce a useful bijection.
}

@@

\hintbox{
	Start by recalling the definition of disjoint union.
	Find separately an injection and a surjection to the disjoint union of interest, and use the CSB theorem.

	Can you find a surjection from $\NN\times J$ to the disjoint union?

	Note that we asked for all $A_j$ to be nonempty.
	What would happen if all (or all but finitely many) $A_j$ were $\emptyset$?
	This offers a clue to how an injection might be constructed.
}

@@

\hintbox{
	Direct construction of a surjection from the disjoint union of the previous proposition to this ordinary union.
}

@@

\hintbox{
	There must be a bijection $f:X\to Y$. Pick an arbitrary $S\subset X$.
	Think about the process of taking the image of $S$ in $f$.
	Is that a function of $S$? Showing injectivity / surjectivity requires you to exploit injectivity / surjectivity of $f$.

	It is probably more efficient to prove the second part first.
}

>>>>

%---------DO NOT EDIT THIS INDENTED SECTION
	% Preamble
	\documentclass[11pt,reqno,oneside,a4paper]{article}
	\usepackage[a4paper,includeheadfoot,left=35mm,right=35mm,top=00mm,bottom=30mm,headheight=40mm]{geometry} %sets up the margins
	\input{../texHead-Proof-Standard} % Use the standard texHead for this module. You should not edit this file.
	\input{../texHead-Proof-Personal} % Use your personal additional macros. You may edit this file.
	%---The following code defines the title, author, and date of the document.
	\title{Practice proofs \#5}
	\author{Anonymous}
	\date{\today}   % Using \today automatically updates to the document's build date
%----------------------------------
%---------IF YOU WANT TO DEFINE YOUR OWN MACROS, YOU CAN DO SO EITHER IN ../texHead-Proof-Personal.tex OR FROM HERE ...

%---------... TO HERE
\begin{document}
\maketitle
\thispagestyle{fancy}

%-----------EDIT FROM HERE

\begin{abstract}
	\input{PracticeProofsStandardAbstract.tex}

	I fitted the whole model solutions onto $1.5$ pages.
\end{abstract}

@@

\begin{proof}
	%--------------EDIT THIS PART--------------%
	% Hint: Directly construct an injection.
	%------------------------------------------%
\end{proof}

@@

\begin{proof}
	%--------------EDIT THIS PART--------------%
	% Hint: Direct proof.
	%------------------------------------------%
\end{proof}

@@

\begin{proof}
	%--------------EDIT THIS PART--------------%
	% Hint: Start by recalling the definition of disjoint union. Find separately an injection and a surjection to the disjoint union of interest, and use the CSB theorem.
	%------------------------------------------%
\end{proof}

@@

\begin{proof}
	%--------------EDIT THIS PART--------------%
	% Hint: Direct construction.
	%------------------------------------------%
\end{proof}

@@

\begin{proof}
	%--------------EDIT THIS PART--------------%
	% Hint: There must be a bijection $f:X\to Y$. Pick an arbitrary $S\subset X$. Think about the process of taking the image of $S$ in $f$. Is that a function of $S$?
	%------------------------------------------%
\end{proof}

\end{document}

### 2018-09-04 practice-proofs/PracticeProofs6.tex
Added files for practice proofs 4-9.

%---------DO NOT EDIT THIS INDENTED SECTION
	% Preamble
	\documentclass[11pt,reqno,oneside,a4paper]{article}
	\usepackage[a4paper,includeheadfoot,left=35mm,right=35mm,top=00mm,bottom=30mm,headheight=40mm]{geometry} %sets up the margins
	\input{../texHead-Proof-Standard} % Use the standard texHead for this module. You should not edit this file.
	\input{../texHead-Proof-Personal} % Use your personal additional macros. You may edit this file.
	%---The following code defines the title, author, and date of the document.
	\title{Practice proofs \#5}
	\author{Anonymous}
	\date{\today}   % Using \today automatically updates to the document's build date
%----------------------------------
%---------IF YOU WANT TO DEFINE YOUR OWN MACROS, YOU CAN DO SO EITHER IN ../texHead-Proof-Personal.tex OR FROM HERE ...

@@

	I fitted the whole model solutions onto $1.5$ pages.
\end{abstract}

\subsection*{Cardinality and subsets}

\begin{prop} \label{prop:SubsetCardinality}
	If $X\subset Y$, then $\# X\leq \# Y$.
\end{prop}

\begin{proof}
	%--------------EDIT THIS PART--------------%
	% Hint: Directly construct an injection.
	%------------------------------------------%
\end{proof}

\subsection*{Countable unions of sets}

@@

\begin{prop} \label{prop:CountableUnions2}
	If, for each $j\in J$, $A_j$ is a nonempty set with cardinality $\#A_j\leq\aleph_0$, and $\#J=\aleph_0$, then
	$$
		\# \bigsqcup_{j\in J} A_j = \aleph_0.
	$$
\end{prop}

\begin{proof}
	%--------------EDIT THIS PART--------------%
	% Hint: Start by recalling the definition of disjoint union. Find separately an injection and a surjection to the disjoint union of interest, and use the CSB theorem.
	%------------------------------------------%
\end{proof}

\begin{prop} \label{prop:CountableUnions3}
	If, for each $j\in J$, $\#A_j\leq\aleph_0$, and $\#J=\aleph_0$, then
	$$
		\# \bigcup_{j\in J} A_j \leq \aleph_0.
	$$
\end{prop}

@@

\subsection*{Cardinality and power sets}

We say that two sets are \emph{equinumerous} if they have the same cardinality. The following proposition says that the operation ``take the power set'' preserves equinumerosity.

\begin{prop} \label{prop:PowerSetsPreserveEquinumerosity}
	Suppose $\# X=\# Y$. Then $\# \power(X)=\# \power(Y)$. Moreover, if $\# X\leq\# Y$, then $\# \power(X)\leq\# \power(Y)$.
\end{prop}

\begin{proof}
	%--------------EDIT THIS PART--------------%
	% Hint: There must be a bijection $f:X\to Y$. Pick an arbitrary $S\subset X$. Think about the process of taking the image of $S$ in $f$. Is that a function of $S$?
	%------------------------------------------%
\end{proof}

>>>>

%---------DO NOT EDIT THIS INDENTED SECTION
	% Preamble
	\documentclass[11pt,reqno,oneside,a4paper]{article}
	\usepackage[a4paper,includeheadfoot,left=35mm,right=35mm,top=00mm,bottom=30mm,headheight=40mm]{geometry} %sets up the margins
	\input{../texHead-Proof-Standard} % Use the standard texHead for this module. You should not edit this file.
	\input{../texHead-Proof-Personal} % Use your personal additional macros. You may edit this file.
	%---The following code defines the title, author, and date of the document.
	\title{Practice proofs \#6}
	\author{Anonymous}
	\date{\today}   % Using \today automatically updates to the document's build date
%----------------------------------
%---------IF YOU WANT TO DEFINE YOUR OWN MACROS, YOU CAN DO SO EITHER IN ../texHead-Proof-Personal.tex OR FROM HERE ...

@@

	I fitted the whole model solutions onto 1 page.
\end{abstract}

@@

\begin{prop} \label{prop:CardinalityUnions2}
	If, for each $j\in J$, $A_j$ is a nonempty set with cardinality $\#A_j\leq\aleph_0$, and $\#J=\aleph_0$, then
	$$
		\# \bigsqcup_{j\in J} A_j = \aleph_0.
	$$
\end{prop}

\begin{proof}
	%--------------EDIT THIS PART--------------%
	% Hint: Start by recalling the definition of disjoint union.
	% Find separately an injection and a surjection to the disjoint union of interest, and use the CSB theorem.
	%------------------------------------------%
\end{proof}

\begin{prop} \label{prop:CardinalityUnions3}
	If, for each $j\in J$, $\#A_j\leq\aleph_0$, and $\#J=\aleph_0$, then
	$$
		\# \bigcup_{j\in J} A_j \leq \aleph_0.
	$$
\end{prop}

@@

### 2018-09-04 practice-proofs/PracticeProofs7.tex
Added files for practice proofs 4-9.

%---------DO NOT EDIT THIS INDENTED SECTION
	% Preamble
	\documentclass[11pt,reqno,oneside,a4paper]{article}
	\usepackage[a4paper,includeheadfoot,left=35mm,right=35mm,top=00mm,bottom=30mm,headheight=40mm]{geometry} %sets up the margins
	\input{../texHead-Proof-Standard} % Use the standard texHead for this module. You should not edit this file.
	\input{../texHead-Proof-Personal} % Use your personal additional macros. You may edit this file.
	%---The following code defines the title, author, and date of the document.
	\title{Practice proofs \#4}
	\author{Anonymous}
	\date{\today}   % Using \today automatically updates to the document's build date
%----------------------------------
%---------IF YOU WANT TO DEFINE YOUR OWN MACROS, YOU CAN DO SO EITHER IN ../texHead-Proof-Personal.tex OR FROM HERE ...

@@

	I fitted the whole model solutions onto a little over 1 page.
\end{abstract}

We explicitly construct a bijection mapping from the unit interval to the whole real line.

\begin{thm} \label{thm:BijectionRInterval}
	Define $f : (0,1) \to \RR$ by
	$$
		f(x) =\frac{1}{1-x} - \frac{1}{x}.
	$$
	The function $f$ is a bijection.
\end{thm}

\begin{proof}
	%--------------EDIT THIS PART--------------%
	% Prove that $f$ is both a surjection and an injection.
	% It will help to show that $f$ is strictly increasing.
	% The intermediate value theorem is also important; if you have not seen it before, then look it up.
	%------------------------------------------%
\end{proof}

>>>>

%---------DO NOT EDIT THIS INDENTED SECTION
	% Preamble
	\documentclass[11pt,reqno,oneside,a4paper]{article}
	\usepackage[a4paper,includeheadfoot,left=35mm,right=35mm,top=00mm,bottom=30mm,headheight=40mm]{geometry} %sets up the margins
	\input{../texHead-Proof-Standard} % Use the standard texHead for this module. You should not edit this file.
	\input{../texHead-Proof-Personal} % Use your personal additional macros. You may edit this file.
	%---The following code defines the title, author, and date of the document.
	\title{Practice proofs \#7}
	\author{Anonymous}
	\date{\today}   % Using \today automatically updates to the document's build date
%----------------------------------
%---------IF YOU WANT TO DEFINE YOUR OWN MACROS, YOU CAN DO SO EITHER IN ../texHead-Proof-Personal.tex OR FROM HERE ...

@@

	I fitted the whole model solutions onto $4/3$ pages.
\end{abstract}

Here we take for granted the set of integers, and all familiar properties of addition, subtraction, and multiplication of integers.
We also take for granted the ``integral domain'' property of integers, which states that $xy = 0$ implies $x = 0$ or $y = 0$, for all integers $x,y$.
Equivalently, if $x \neq 0$ and $y \neq 0$ then $xy \neq 0$.
This implies the cancellation property: if $x,y,z \in \ZZ$, and $z \neq 0$, and $xz = yz$, then $x = y$.

A \emph{fraction} will mean an ordered pair $(x,y) \in \ZZ^2$ such that $y \neq 0$. Let $F$ be the set of fractions.
Consider the relation $\sim$ on $F$ given by the rule
$$
	(x,y) \sim (u,v) \text{ means that } xv = yu.
$$
The point of $\sim$ is that if two fractions obey $(x,y)\sim(u,v)$, then they are two expressions of the same rational number.
For example, $(2,4)\sim(12,24)$, and they both correspond to the rational number that we are used to representing $\frac{1}{2}$.

\begin{thm} \label{thm:EquivaentFractions}
	The relation $\sim$ is an equivalence relation on the set $F$.
\end{thm}

\begin{proof}
	%--------------EDIT THIS PART--------------%
	% Hint: Direct proof that $\sim$ satisfies each of the three properties of an equivalence relation.
	%------------------------------------------%
\end{proof}

### 2018-09-04 practice-proofs/PracticeProofs9.tex
Added files for practice proofs 4-9.

%---------DO NOT EDIT THIS INDENTED SECTION
	% Preamble
	\documentclass[11pt,reqno,oneside,a4paper]{article}
	\usepackage[a4paper,includeheadfoot,left=35mm,right=35mm,top=00mm,bottom=30mm,headheight=40mm]{geometry} %sets up the margins
	\input{../texHead-Proof-Standard} % Use the standard texHead for this module. You should not edit this file.
	\input{../texHead-Proof-Personal} % Use your personal additional macros. You may edit this file.
	%---The following code defines the title, author, and date of the document.
	\title{Practice proofs \#7}
	\author{Anonymous}
	\date{\today}   % Using \today automatically updates to the document's build date
%----------------------------------
%---------IF YOU WANT TO DEFINE YOUR OWN MACROS, YOU CAN DO SO EITHER IN ../texHead-Proof-Personal.tex OR FROM HERE ...

@@

	I fitted the whole model solutions onto $4/3$ pages.
\end{abstract}

Here we take for granted the set of integers, and all familiar properties of addition, subtraction, and multiplication of integers.
We also take for granted the ``integral domain'' property of integers, which states that $xy = 0$ implies $x = 0$ or $y = 0$, for all integers $x,y$.
Equivalently, if $x \neq 0$ and $y \neq 0$ then $xy \neq 0$.
This implies the cancellation property: if $x,y,z \in \ZZ$, and $z \neq 0$, and $xz = yz$, then $x = y$.

A \emph{fraction} will mean an ordered pair $(x,y) \in \ZZ^2$ such that $y \neq 0$. Let $F$ be the set of fractions.
Consider the relation $\sim$ on $F$ given by the rule
$$
	(x,y) \sim (u,v) \text{ means that } xv = yu.
$$
The point of $\sim$ is that if two fractions obey $(x,y)\sim(u,v)$, then they are two expressions of the same rational number.
For example, $(2,4)\sim(12,24)$, and they both correspond to the rational number that we are used to representing $\frac{1}{2}$.

\begin{thm} \label{thm:EquivaentFractions}
	The relation $\sim$ is an equivalence relation on the set $F$.
\end{thm}

\begin{proof}
	%--------------EDIT THIS PART--------------%
	% Hint: Direct proof that $\sim$ satisfies each of the three properties of an equivalence relation.
	%------------------------------------------%
\end{proof}

>>>>

%---------DO NOT EDIT THIS INDENTED SECTION
	% Preamble
	\documentclass[11pt,reqno,oneside,a4paper]{article}
	\usepackage[a4paper,includeheadfoot,left=35mm,right=35mm,top=00mm,bottom=30mm,headheight=40mm]{geometry} %sets up the margins
	\input{../texHead-Proof-Standard} % Use the standard texHead for this module. You should not edit this file.
	\input{../texHead-Proof-Personal} % Use your personal additional macros. You may edit this file.
	%---The following code defines the title, author, and date of the document.
	\title{Practice proofs \#9}
	\author{Anonymous}
	\date{\today}   % Using \today automatically updates to the document's build date
%----------------------------------
%---------IF YOU WANT TO DEFINE YOUR OWN MACROS, YOU CAN DO SO EITHER IN ../texHead-Proof-Personal.tex OR FROM HERE ...

@@

	I fitted the whole model solutions onto 2 pages.
\end{abstract}

We argue that real multiplication, as defined through multiplication of rational Cauchy sequences, satisfies the corresponding five field axioms.

\begin{lem} \label{lem:ExistsNonzeroCauchySequence}
	Suppose that $x\in\RR\setminus\{0_\RR\}$.
	Then there is a rational $M>0$ and a Cauchy sequence $(x_n)_{n\in\NN}$ such every term has $|x_n|>M$ and $(x_n)_{n\in\NN}$ belongs to the equivalence class $x$.
\end{lem}

\begin{proof}
	%--------------EDIT THIS PART--------------%
	% Hint: The idea is to argue that there is a rational Cauchy sequence in $x$ for which at most finitely many terms are less than $M$.
	% Try contradiction; you should end up proving $x=0_\RR$.
	% After that, you can fix the finitely many ``problem'' terms without changing the equivalence class of your Cauchy sequence.
	%------------------------------------------%
\end{proof}

\begin{thm} \label{thm:RealMultiplication}
	Real multiplication, defined as the descent of multiplication of rational Cauchy sequences, obeys field axioms~\textup{(6)--(10)}.
\end{thm}

\begin{proof}
	%--------------EDIT THIS PART--------------%
	% Hint: Axioms~(6)--(9) essentially follow from the corresponding properties for rational numbers.
	% For axiom~(10), the tricky part is showing that the sequence you want to represent the multiplicative inverse is actually a Cauchy sequence.
	% It might be easiest to start by structuring the proof as if you have a magical lemma that guarantees the sequence is Cauchy, then go back and fill the gap, using lemma~\ref{lem:ExistsNonzeroCauchySequence} and some ingenuity.
	%------------------------------------------%
\end{proof}
